Untitled

### 2023-11-26 code/analysis_Redo.Rmd
test
update usethis
changing figs

@@

@@

summary(lm(data = df.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Assets ~ Treated*year.rel))$coeff[4,]
summary(lm(data = df.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Staff ~ Treated*year.rel))$coeff[4,]
summary(lm(data = df.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Sites.y ~ Treated*year.rel))$coeff[4,]

@@

did2s(
      data = df.profit %>% mutate(pc = ngla_net_gain_loss / ngla_expense * 10) %>% filter(!is.na(pc)) , 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * pc) + I(Tx * pc^2) ,
        cluster_var = "STATE",
      verbose = FALSE
    )

>>>>

p.desc <- ggarrange(plot1, plot0, ncol = 2)

ggsave(filename = "Picture1h.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p.desc, width = 16, height = 9)

@@

p0 <- ggarrange(
  event_study(data = df.core, 
  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients"), 
event_study(data = df.core, 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
event_study(data = df.core, 
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, ncol = 3 ) 
p0

ggsave(filename = "Picture3ah.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 17, height = 9)
```

@@

#summary(lm(data = df.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Assets ~ Treated*year.rel))$coeff[4,]
summary(lm(data = df.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Staff ~ Treated*year.rel))$coeff[4,]
summary(lm(data = df.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Sites.y ~ Treated*year.rel))$coeff[4,]

@@

# did2s(
#       data = df.profit %>% mutate(pc = ngla_net_gain_loss / ngla_expense * 10) %>% filter(!is.na(pc)) , 
#       yname = "Qcomp", 
#       treatment = "Tx",
#         first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
#         second_stage = ~ i(Tx, ref = FALSE) + I(Tx * pc) + I(Tx * pc^2) ,
#         cluster_var = "STATE",
#       verbose = FALSE
#     )
